Utilitarianism

### 2016-01-19 writing_in_ethics/paper_one.tex
so much work
editing paper

\begin{document}
\drafth{}
\inlinetitle

The theory of Utilitarianism can be used to quantitatively analyze various situations that arise in day to day life; it can be applied the scenario presented in \textit{Ethics for the Information Age} that concerns Alexis' education. In order to analyze the situation and determine whether or not her actions were ethically ``good" or ``bad", the total utility change needs to be calculated. Alexis' actions can be considered ethically good if the benefit of her actions exceed the harms. The situation can be analyzed using both Rule and Act Utilitarianism.

@@

Both Rule and Act Utilitarianism provide interesting views on the ethical decision that Alexis made. Under Rule Utilitarianism, Alexis' decision was ethically wrong; under Act Utilitarianism, her decision was ethically right. Both of the methods used to analyze the situation provide a method to determine whether or not Alexis made the right choice; nether Rule nor Act Utilitarianism are absolute.

\newpage
\printbibliography

>>>>

% \linenumbers

\begin{document}
\drafth{}
\inlinetitle
\begin{linenumbers}
The theory of Utilitarianism can be used to quantitatively analyze various situations that arise in day to day life. It can be used to analyze the scenario presented in \textit{Ethics for the Information Age} in which a promising high school student, Alexis, steals login information in order to use a computer to which she does not have access. Alexis' situation can be analyzed under both Rule and Act Utilitarianism, which both require a numerical value to be computed based on the actions of an individual. In Alexis' case, there is no clear unit that can be assigned to the value of her actions; rather, the overall general outcome can be used to gauge the utility of Alexis' actions.

@@

Both Rule and Act Utilitarianism provide interesting views on the ethical decision that Alexis made. Under Rule Utilitarianism, Alexis' decision was ethically wrong; under Act Utilitarianism, her decision was ethically right. Both of the methods used to analyze the situation provide a method to determine whether or not Alexis made the right choice; nether Rule nor Act Utilitarianism are absolute.
\end{linenumbers}
\newpage
\printbibliography
